Blueprint

### 2020-11-26 blueprint.tex
updates blueprint

\title{What is a Scheme in Algebraic Geometry?}
\author{Anthony Bordg}
\date{\today}
\maketitle

@@

\begin{definition}[local ring]
Let $\mathfrak{p}$ be a prime ideal of $R$ and $S$ the complement of $\mathfrak{p}$ in $R$. The local ring of $R$ at $\mathfrak{p}$, denoted $R_{\mathfrak{p}}$, is $S^{-1} R$. 	
\end{definition}

@@

@@

\begin{definition}[morphism of locally ringed spaces]

\end{definition}

\begin{definition}[affine scheme]
	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic to the spectrum $(Spec R, \mathscr{O}_R)$ for some ring $R$. 
\end{definition}

>>>>

\title{Blueprint}	
%\title{What is a Scheme in Algebraic Geometry?}
\author{Anthony Bordg}
\date{\today}
\maketitle

@@

\begin{definition}[local ring at a prime ideal] \label{localringat}
	Let $\mathfrak{p}$ be a prime ideal of $R$ and $S$ the complement of $\mathfrak{p}$ in $R$. The local ring of $R$ at $\mathfrak{p}$, denoted $R_{\mathfrak{p}}$, is $S^{-1} R$. 
\end{definition}

@@

\begin{definition}[maximal ideal]
	Let $\mathfrak{m}$ be an ideal of $R$. The ideal $\mathfrak{m}$ is maximal if $\mathfrak{m} \neq R$ and there is no ideal $\mathfrak{a} \neq R$ such that $\mathfrak{m} \subset \mathfrak{a}$.
\end{definition}

\begin{definition}[local ring]
	A ring is a local ring if it is commutative and it has a unique maximal ideal. 	
\end{definition}

\begin{ex}
	Prove $R_{\mathfrak{p}}$ \ref{localringat} is a local ring.
\end{ex}

\begin{definition}[local homomorphism]
	Let $A$ and $B$ be two local rings and $\mathfrak{m}_A$, $\mathfrak{m}_B$ their respective maximal ideals. \\
	A local homomorphism $f: A \rightarrow B$ is a morphism of rings such that $f^{-1} (\mathfrak{m}_B) = \mathfrak{m}_A$. 
\end{definition}

@@

\begin{cons}

\end{cons}

\begin{definition}[morphism of locally ringed spaces]
	A morphism of locally ringed spaces from $(X, \mathscr{O}_X)$ to $(Y, \mathscr{O}_Y)$ is a morphism $(f, \phi_f)$ between ringed spaces such that the induced map of local rings $\phi_{f, x}: (\mathscr{O}_Y)_{f(x)} \rightarrow (\mathscr{O}_X)_x$ is a local homomorphism for every $x \in X$.  
\end{definition}

\begin{definition}[affine scheme]
	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic (as a locally ringed space) to the spectrum $(Spec R, \mathscr{O}_R)$ for some ring $R$. 
\end{definition}
